---
title: "HGG survival Analysis"
output: html_document
date: "2026-01-20"
#includes dubois data, supplemental table (although may not be most updated version) and updated HGG NOS from CBTN
#removed HGNET tumors
# TODO: convert to ipynb
---
#Survival Graph - All HGG
#Load packages and data
```{r}
library(readxl)
library(dplyr)
library(survival)
library(survminer)
library(tidyr)
library(ggplot2)
library(grid)
library(extrafont)
library(svglite)
library(ComplexHeatmap)
library(circlize)
library(patchwork)


import_hgg_data = function(path = "../../manuscript/collaborators/Rishaan/pHGG/pHGG_Survival_Data_Merged.xlsx"){
    # 2026/3 Changelog: wrap in function, censor at 5y, drop HGNET, cleanup (drop unused transformations, drop_na), add ecDNA_status and amplified
    df <- read_excel(path)
    df <- df %>% 
        rename_with(tolower) %>%
        drop_na(os_months,os_status) %>%
        filter(cancer_subclass != 'HGNET') %>%
        mutate(
            os_status = tolower(os_status),
            os_event = case_when(
                os_status %in% c("deceased", "dead") ~ 1,
                os_status %in% c("alive", "living") ~ 0,
                TRUE ~ NA_real_),
            os_event = if_else(os_months <= 60, os_event, 0),
            os_months = if_else(os_months < 60, os_months, 60),
            amplicon_class = case_when(
              amplicon_class %in% c("Chromosomal", "intrachromosomal") ~ "chromosomal",
              TRUE ~ amplicon_class
            ),
            ecDNA_status = ifelse(amplicon_class == "ecDNA","ecDNA+","ecDNA-"),
            amplified = ifelse(amplicon_class %in% c('ecDNA','chromosomal'),"amp+","amp-")
        ) %>% 
        select(-os_status)
}

factorize = function(df){
    # convert string columns to factors.
    transformations = list(
        cancer_subclass = . %>% factor(),
        cancer_subclass2 = . %>% factor(),
        H3G34 = . %>% factor(),
        H3K27 = . %>% factor(),
        TP53 = . %>% factor(),
        IDH = . %>% factor(),
        hgg_subtype = . %>% factor() %>% relevel(ref="H3WT"),
        amplicon_class = . %>% factor() %>% relevel(ref="no amplification"),
        ecDNA_status = . %>% factor() %>% relevel(ref="ecDNA-"),
        chromosomal_amp = . %>% factor() %>% relevel(ref="amp-"),
        amplified = . %>% factor() %>% relevel(ref="amp-")
    )
    df <- reduce(names(transformations), function(df, col) {
        if (!col %in% names(df)) return(df)
        mutate(df, across(all_of(col), transformations[[col]]))
    }, .init = df)
    return(df)
}
# Usage:
df = import_hgg_data() %>% factorize
print(table(df$amplicon_class))
print(table(df$os_event))
```
```{r}
# Reusable plotting functions using ggsurvfit

km_plot <- function(survObj,outfile=NULL,colors=NULL){
  ## generate a KM plot from a KM regression object (survival::survfit)
  strata_names = names(survObj$strata)
  labels = setNames(strata_names %>% str_replace("^.*=",""),strata_names)
  if (is.null(colors)){
    if (length(survObj$n) == 2){
    colors = setNames(c('red', 'blue'), strata_names)
    } else if (length(survObj$n) == 3){
    colors = setNames(c('dodgerblue','magenta','red'), strata_names)
    } else {
    colors = setNames(RColorBrewer::brewer.pal(length(survObj$n), "Dark2"), strata_names)
    }
  }
  plt <- survObj %>% 
   ggsurvfit(linewidth=0.5) +
   labs(x = 'Follow-up time (Months)',
        y = 'Overall Survival') +
   scale_color_manual(values = colors,
                      labels = labels) +
   scale_fill_manual(values = colors,
                     labels = labels) +
   scale_y_continuous(limits=c(0, 1))+
   add_censor_mark(size = .5, alpha = 1) +
   add_risktable(risktable_stats = "n.risk", size=2,
                 theme = theme_risktable_default(axis.text.y.size = 7,
                                    plot.title.size = 7)) +
   add_risktable_strata_symbol(size=8) + 
   theme_classic(base_size=7, base_family="Arial",) +
   theme(axis.text = element_text(size=7,colour="black"),
         legend.position = "bottom",
   )
  if (length(survObj$n) <=3){
    plt <- plt + add_confidence_interval()
    height=3.5
  } else{
    height=4
  }
  
  if(!is.null(outfile)){
    pngName = paste(outfile, ".png", sep="")
    svgName = paste(outfile, ".svg", sep = "")
    ggsave(path=".", device="png", filename=pngName, width=3, height=height, units='in')
    ggsave(path=".", device="svg", filename=svgName, width=3, height=height, units='in')
  }
  return(plt)
}
cox_plot <- function(coxobj,outfile=NULL,width=3,height=6){
  ## generate a forest plot from a Cox regression object (survival::coxph)
  zph <-cox.zph(coxobj) 
  print(zph)
  #create forest plots
  plt <- ggforest(coxobj,data=model.frame(coxobj)) +
        theme_classic(base_size=7, base_family="Arial") +
        theme(axis.text = element_text(size=7,colour="black"),
              plot.title = element_text(size=7))

  if(!is.null(outfile)){
    pngName = paste(outfile, ".png", sep="")
    svgName = paste(outfile, ".svg", sep = "")
    ggsave(path=".", device="png", filename=pngName, width=width, height=height, units='in')
    ggsave(path=".", device="svg", filename=svgName, width=width, height=height, units='in')
  }
  return(plt)
}
dir.create('hgg', showWarnings = FALSE)
```
```{r}
df = import_hgg_data() %>% factorize
km_fit <- survfit(Surv(os_months, os_event) ~ amplicon_class, data = df)

km_plot(km_fit,"hgg/KM_Survival_AmpliconClass")
#km_plot <- ggsurvplot(
#  fit = km_fit,
#  data = df,
#  conf.int = TRUE,
#  risk.table = TRUE,
#  palette = c("#E41A1C", "#377EB8", "#4DAF4A"),
#  ggtheme = theme_bw() + theme(plot.title = element_text(hjust = 0.5)),
#  title = "pHGG Survival by Amplicon Class",
#  xlab = "Overall Survival (Months)",
#  ylab = "Survival Probability",
#  risk.table.height = 0.25,
#  risk.table.y.text.col = TRUE,
#  risk.table.y.text = FALSE,
#  font.main = c(16, "bold", "black"),
#  font.x = c(14, "bold", "black"),
#  font.y = c(14, "bold", "black")
#)
#options(repr.plot.width = 12, repr.plot.height = 8)
#print(km_plot)
#pdf("KM_Survival_AmpliconClass.pdf", width = 12, height = 8)
#print(km_plot)
#dev.off()

# Print log-rank test p-values
logrank <- pairwise_survdiff(Surv(os_months, os_event) ~ amplicon_class, data = df, p.adjust.method = "BH")
logrank_df <- as.data.frame(as.table(as.matrix(logrank$p.value)))
p_ecDNA <- logrank_df %>% filter(Var1 == "ecDNA" | Var2 == "ecDNA") %>% mutate(comparison = paste(Var1, "vs", Var2), p_value = signif(Freq, 3)) %>%
  select(comparison, p_value)
print(logrank)
pval_labels <- paste0(p_ecDNA$comparison, " (p=", p_ecDNA$p_value, ")")
cat(paste0(p_ecDNA$comparison, ": ", p_ecDNA$p_value, collapse = "\n"))
```

```{r}
## ecDNA+/- KM curves.
## now nominally nonsignificant (p=0.065).

df <- import_hgg_data() %>% factorize
formula = Surv(os_months, os_event) ~ ecDNA_status
km_fit <- survfit(formula, data = df)
logrank <- pairwise_survdiff(formula, data = df, p.adjust.method = "BH")
logrank_df <- as.data.frame(as.table(as.matrix(logrank$p.value)))
p_ecDNA <- logrank_df %>%
  filter((Var1 == "ecDNA+" & Var2 == "ecDNA-") | (Var1 == "ecDNA-" & Var2 == "ecDNA+")) %>%
  mutate(
    comparison = paste(Var1, "vs", Var2),
    p_value = signif(Freq, 3)
  ) %>%
  select(comparison, p_value)
pval_num <- p_ecDNA$p_value  
summary_table <- tableGrob(
  p_ecDNA,
  rows = NULL,
  theme = ttheme_minimal(base_size = 12)
)
print(logrank)

km_plot(km_fit,"hgg/pHGG_Survival_ecDNA_vs_ecDNAminus")
#km_plot <- ggsurvplot(
#  fit = km_fit,
#  data = df,
#  conf.int = TRUE,
#  risk.table = TRUE,
#  palette = c("#E41A1C", "#377EB8"),  # red, blue
#  ggtheme = theme_bw() + theme(plot.title = element_text(hjust = 0.5)),
#  title = "pHGG Survival: ecDNA+ vs ecDNA-",
#  xlab = "Overall Survival (Months)",
#  ylab = "Survival Probability",
#  risk.table.height = 0.25,
#  risk.table.y.text.col = TRUE,
#  risk.table.y.text = FALSE,
#  font.main = c(16, "bold", "black"),
#  font.x = c(14, "bold", "black"),
#  font.y = c(14, "bold", "black"),
#  pval = TRUE,                
#  pval.method = FALSE,        
#  pval.coord = c(0, 0.03),    
#  pval.size = 6
#)
#km_plot$plot <- km_plot$plot +
#  annotate(
#    "text",
#    x = max(df$os_months) * 0.75,
#    y = 0.15,
#    label = paste0("Log-rank p = ", pval_num),
#    size = 5
#  )
#pdf("pHGG_Survival_ecDNA_vs_ecDNAminus.pdf", width = 12, height = 12)
#print(km_plot$plot) 
#print(km_plot$table)
#grid.newpage()
#grid.draw(summary_table) 
#dev.off()
```
#Cox regression with subclasses
```{r}
## Reusable functions for annotating subgroups, mutations, and interaction terms.
## Note that ggforest can't plot interaction terms generated with interaction(), hence the add_h3k27_interactions function to explicitly add those to the data.
## 2026/3 Changelog: 
# Other -> IHG, IDH, NOS
# Bugfix mutation detection logic - NOS classes shouldn't be set to NA, and one of them is TP53
# delete redundant droplevels, KM plots, H3WT variable
# rename combined_cancer_subclass -> hgg_subtype

#Combining similar HGG subclasses
aggregate_hgg_mutations = function(df){
    h3k27_classes <- c("DMG_H3K27", "DMG_H3K27M", "HGG_H3K27", "DMG_H3K27_TP53")
    h3wt_classes  <- c("HGG_H3WT", "HGG_H3WT_TP53")
    h3g34_classes <- c("DHG_H3G34", "DHG_H3G34_TP53", "HGG_H3G34")
    collapse_to_other <- c("IHG_ALK", "IHG_NRTK", "IHG_ROS1_TP53", "IHGNOS")
    df = df %>%
        mutate(
            hgg_subtype = case_when(
                cancer_subclass %in% collapse_to_other ~ "IHG",
                cancer_subclass %in% h3k27_classes ~ "H3K27-altered",
                cancer_subclass %in% h3wt_classes  ~ "H3WT", ###
                cancer_subclass %in% h3g34_classes  ~ "H3G34-altered",
                cancer_subclass == 'HGG_IDH_TP53' ~ 'IDH',
                cancer_subclass == 'HGG_NOS' ~ 'NOS',
                TRUE ~ cancer_subclass #stop('unknown cancer_subclass')
            ),
            TP53 = ifelse(grepl("TP53", cancer_subclass, ignore.case = TRUE),1,0),
            H3K27 = ifelse(grepl("H3K27", cancer_subclass, ignore.case=TRUE),1,0),
            H3G34 = ifelse(grepl("H3G34", cancer_subclass, ignore.case=TRUE),1,0),
            IDH = ifelse(grepl("IDH", cancer_subclass, ignore.case=TRUE),1,0),
        ) %>%
        factorize() %>% 
        droplevels()
}

add_h3k27_interactions = function(df){
    # Create a interaction terms for h3k27 x amplification; and, because ggforest can't plot interactions, manually
    # add these as independent variables
    h3k27_labels = c("1"="H3K27mut","0"="H3K27wt")
    ampclass_labels = c("no amplification"="nfa","chromosomal"="chr","ecDNA"="ecDNA")
    df %>% mutate(
        h3k27_x_amp = ifelse(H3K27==1 & amplified == 'amp+',1,0),
        h3k27_x_ecDNA = ifelse(H3K27==1 & ecDNA_status == 'ecDNA+',1,0),
        h3k27_x_chr = ifelse(H3K27==1 & amplicon_class == 'chromosomal',1,0),
        ecDNA_H3K27 = interaction(ecDNA_status, fct_relabel(H3K27,~ h3k27_labels[.x]), drop = TRUE),
        ampclass_H3K27 = interaction(
            fct_relabel(amplicon_class,~ ampclass_labels[.x]),
            fct_relabel(H3K27,~ h3k27_labels[.x]), 
            drop = TRUE)
    )
}

# Usage:
df <- import_hgg_data() %>% factorize %>% aggregate_hgg_mutations %>% add_h3k27_interactions
subclass_counts <- df %>% count(hgg_subtype)
print(subclass_counts)
df %>% head
```
```{r}
#Cox model for cancer subclass combined
#Question: Does ecDNA independently affect survival after mutations
#Answers: “Is ecDNA prognostic independent of histone subtype?”. Answer is no, globally across all subtypes
# 2026/03 Changelog:
# - add TP53 term
# - chomosomal_amp -> amplified

cox_model <- coxph(
  Surv(os_months, os_event) ~ ecDNA_status + amplified + hgg_subtype + TP53,
  data = df
)

cox_plot(cox_model,width=6,height=6)
#pdf("pHGG_Survival_KM_and_Cox.pdf", width = 12, height = 8)
#print(km_plot$plot)
#print(km_plot$table)
#ggforest(cox_model, data = as.data.frame(df))
#dev.off()

# Alternately, using amplicon_class. Same model, different reference levels.
cox_model <- coxph(
  Surv(os_months, os_event) ~ amplicon_class + hgg_subtype + TP53,
  data = df
)

cox_plot(cox_model,outfile="hgg/pHGG_Cox_subgroups_p53",width=6,height=4.5)
#ggforest(cox_multi, data = as.data.frame(df))
#dev.off()
```
```{r}
#Cox model for cancer subclass combined. Question: Does ecDNA;s effect depend on mutation status (is ecDNA worse in H3K27 tumors than in H3WT tumors)
#interpretation: ecDNA is prognostic in gliomas lacking H3K27 alteration, but its effect is neutralized in the context of H3K27-altered disease, where baseline risk is already extreme.

df = import_hgg_data() %>% factorize %>% aggregate_hgg_mutations %>% add_h3k27_interactions

cox_interaction <- coxph(
    Surv(os_months, os_event) ~ amplicon_class + hgg_subtype + TP53 + h3k27_x_ecDNA + h3k27_x_amp,
    data = df
)
summary(cox_interaction)

#fit <- survfit(Surv(os_months, os_event) ~ ecDNA_H3K27, data = df)

#ggsurvplot(
#  fit,
#  data = df,
#  pval = TRUE,
#  risk.table = TRUE,
#  legend.title = "ecDNA × H3 status",
#  legend.labs = levels(df$ecDNA_H3K27)
#)

ggforest(cox_interaction, data = as.data.frame(df))

#Cox model for H3K27 interaction with amplicon_class
cox_interaction <- coxph(
Surv(os_months, os_event) ~ amplicon_class * H3K27 + chromosomal_amp + H3G34 + TP53,
data = df
)
summary(cox_interaction)
#ggforest(cox_interaction, data = as.data.frame(df))
cox_plot(cox_interaction,outfile="hgg/pHGG_Cox_interaction_term",width=6,height=5)

hr_with_ci <- function(fit, terms) {
  # Function to calculate hazards relative to levels other than reference
  coefs <- coef(fit)
  v <- vcov(fit)
  
  log_hr <- sum(coefs[terms])
  se <- sqrt(sum(v[terms, terms]))
  
  list(
    hr  = exp(log_hr),
    ci  = exp(log_hr + c(-1, 1) * 1.96 * se),
    p   = 2 * pnorm(-abs(log_hr / se))
  )
}
# hazard for ecDNA given H3K27M-altered
hr_with_ci(cox_interaction,c('amplicon_classecDNA','h3k27_x_ecDNA'))
```
```{r}
# KM, ecDNA x H3K27
# (Not currently using this in the manuscript)
fit <- survfit(Surv(os_months, os_event) ~ ecDNA_H3K27, data = df)
ggsurvplot(
  fit,
  data = df,
  pval = TRUE,
  risk.table = TRUE,
  legend.title = "ecDNA × H3 status",
  legend.labs = levels(df$ecDNA_H3K27)
)

# KM, amp_class x H3K27
fit <- survfit(Surv(os_months, os_event) ~ ampclass_H3K27, data = df)
plt = ggsurvplot(
  fit,
  data = df,
  pval = TRUE,
  risk.table = TRUE,
  legend.title = "amp. class ×\nH3 status",
  legend.labs = levels(df$ampclass_H3K27)
)
plt

logrank <- pairwise_survdiff(Surv(os_months, os_event) ~ ampclass_H3K27, data = df, p.adjust.method = "BH") ## 
# get colors with ggplot_build(plt$plot)$data[[1]] %>% group_by(group) %>% slice(1) %>% pull(colour)
colors=setNames(c('#F8766D','#B79F00','#00BA38','#00BFC4','#619CFF','#F564E3'),names(fit$strata))
km_plot(fit,"hgg/pHGG_Survival_ecDNA_x_h3k27",colors=colors)
print(logrank)

# Confusion matrix for p-values, since pairwise across six comparisons is a lot
asdf = Heatmap(
    logrank$p.value,
    cluster_rows = FALSE,
    cluster_columns = FALSE,
    cell_fun = function(j, i, x, y, w, h, col) { # add text to each grid
        grid.text(logrank$p.value[i, j] %>% round(4), x, y)},
    na_col = "white",
    row_names_side = "left",
    show_heatmap_legend = FALSE,
    col = colorRamp2(c(0,0.05, 1), c("steelblue", "skyblue","white")),
)
options(repr.plot.width = 3, repr.plot.height = 3)
asdf
svglite("hgg/pHGG_pvals_ecDNA_x_h3k27.svg", width = 5, height = 5)
draw(asdf)
dev.off()
```

```{r}
## Side-by-side plots of KM, amplicon_class stratified by H3K27

df_H3K27neg <- df %>% filter(H3K27 == 0)
fit_neg <- survfit(Surv(os_months, os_event) ~ amplicon_class,
                   data = df_H3K27neg)
p1 <- ggsurvplot(
  fit_neg,
  data = df_H3K27neg,
  risk.table = TRUE,
  pval = TRUE,
  conf.int = FALSE,
  legend.title = "ecDNA",
  legend.labs = c("ecDNA", "intrachromosomal", "no amplification"),
  title = "H3K27– tumors"
)

df_H3K27pos <- df %>% filter(H3K27 == 1)
fit_pos <- survfit(Surv(os_months, os_event) ~ amplicon_class,
                   data = df_H3K27pos)
p2 <- ggsurvplot(
  fit_pos,
  data = df_H3K27pos,
  risk.table = TRUE,
  pval = TRUE,
  conf.int = FALSE,
  legend.title = "ecDNA",
  legend.labs = c("ecDNA", "intrachromosomal", "no amplification"),
  title = "H3K27-altered tumors"
)

#library(patchwork)
p1$plot + p2$plot

#save figure
ggsave("hgg/KM_ampliconclass_by_H3K27.pdf", width = 10, height = 5)


## Side-by-side plots of KM, ecDNA_status stratified by H3K27

df_H3K27neg <- df %>% filter(H3K27 == 0)
fit_neg <- survfit(Surv(os_months, os_event) ~ ecDNA_status,
                   data = df_H3K27neg)
p1 <- ggsurvplot(
  fit_neg,
  data = df_H3K27neg,
  risk.table = TRUE,
  pval = TRUE,
  conf.int = FALSE,
  legend.title = "ecDNA",
  legend.labs = c("ecDNA−", "ecDNA+"),
  title = "H3K27– tumors"
)

df_H3K27pos <- df %>% filter(H3K27 == 1)
fit_pos <- survfit(Surv(os_months, os_event) ~ ecDNA_status,
                   data = df_H3K27pos)
p2 <- ggsurvplot(
  fit_pos,
  data = df_H3K27pos,
  risk.table = TRUE,
  pval = TRUE,
  conf.int = FALSE,
  legend.title = "ecDNA",
  legend.labs = c("ecDNA−", "ecDNA+"),
  title = "H3K27-altered tumors"
)
#library(patchwork)

p1$plot + p2$plot

#save figure
ggsave("hgg/KM_ecDNA_by_H3K27.pdf", width = 10, height = 5)

## (OSC removed duplicate Cox models already constructed above)

```
#Making combined forest plot with the data
## OSC bit confused, isn't this the same as a Cox model you created above, but making the forest plot yourself instead of using ggforest? 
```{r}
#Fit model
cox_ecDNA_adj <- coxph(
Surv(os_months, os_event) ~ ecDNA_status + H3K27 + H3G34 + TP53,
  data = df
)
#tidy model output
library(broom)
forest_df <- tidy(cox_ecDNA_adj, exponentiate = TRUE, conf.int = TRUE) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = recode(
      term,
      "ecDNA_status1" = "ecDNA+",
      "H3K271" = "H3K27-altered",
      "H3G341" = "H3G34-altered",
      "TP531"  = "TP53-altered"
    )
  )
#Forest plot
library(ggplot2)

p_forest <- ggplot(
  forest_df,
  aes(x = estimate, y = reorder(term, estimate))
) +
  geom_vline(xintercept = 1, linetype = "dashed", color = "grey40") +
  geom_point(size = 4) +
  geom_errorbar(
    aes(xmin = conf.low, xmax = conf.high),
    height = 0.25,
    linewidth = 1,
    orientation = "y"
  ) +
  scale_x_log10() +
  labs(
    title = "Multivariable Cox Model for Overall Survival",
    subtitle = "Hazard ratios adjusted for mutation status",
    x = "Hazard Ratio (log scale)",
    y = NULL
  ) +
  theme_minimal(base_size = 28) +
  theme(
    plot.title = element_text(face = "bold", size = 32),
    axis.text = element_text(size = 24)
  )

ggsave(
  "hgg/Forest_Cox_ecDNA_adjusted.png",
  p_forest,
  width = 13.33,
  height = 7.5,
  dpi = 300
)
```
# Combined forest plot comparing hazards of different Cox models
```{r}
cox_unadj <- coxph(Surv(os_months, os_event) ~ ecDNA_status, data = df)

cox_adj <- coxph(
  Surv(os_months, os_event) ~ ecDNA_status + H3K27 + H3G34 + TP53,
  data = df
)

cox_interaction <- coxph(
  Surv(os_months, os_event) ~ ecDNA_status * H3K27 + H3G34 + TP53,
  data = df
)

#extract ecDNA effect from each model
extract_ecDNA <- function(model, label) {
  tidy(model, exponentiate = TRUE, conf.int = TRUE) %>%
    filter(term == "ecDNA_status1") %>%
    mutate(model = label)
}

forest_multi <- bind_rows(
  extract_ecDNA(cox_unadj, "Unadjusted"),
  extract_ecDNA(cox_adj, "Adjusted for mutations"),
  extract_ecDNA(cox_interaction, "With H3K27 interaction")
)

#Forest plot
p_forest_multi <- ggplot(
  forest_multi,
  aes(x = estimate, y = model)
) +
  geom_vline(xintercept = 1, linetype = "dashed", color = "grey40") +
  geom_point(size = 4) +
  geom_errorbarh(
    aes(xmin = conf.low, xmax = conf.high),
    height = 0.25,
    linewidth = 1
  ) +
  scale_x_log10() +
  labs(
    title = "Effect of ecDNA on Overall Survival Across Models",
    x = "Hazard Ratio (log scale)",
    y = NULL
  ) +
  theme_minimal(base_size = 28) +
  theme(
    plot.title = element_text(face = "bold", size = 32),
    axis.text = element_text(size = 24)
  )

ggsave(
  "hgg/Forest_ecDNA_ModelComparison.png",
  p_forest_multi,
  width = 20.33,
  height = 10,
  dpi = 300
)

forest_df
forest_multi
```
#Revision of survival curve with interaction terms so easier to interpret plots
## OSC think these are duplicates of models specified above, lmk if not the case
```{r}
df <- df %>%
  mutate(
    H3_group = factor(
      ifelse(H3K27 == 1, "H3K27M", "WT"),
      levels = c("WT", "H3K27M")
    ),
    ecDNA_group = factor(
      ifelse(group2 == "ecDNA+", "ecDNA+", "ecDNA−"),
      levels = c("ecDNA−", "ecDNA+")
    )
  )

df <- df %>%
  mutate(
    strata_group = interaction(H3_group, ecDNA_group, drop = TRUE)
  )

table(df$strata_group)


fit2 <- survfit(
  Surv(os_months, os_event) ~ strata_group,
  data = df
)

fit2$strata

options(repr.plot.width = 12, repr.plot.height = 8)

ggsurvplot(
  fit2,
  data = df,
  pval = TRUE,
  risk.table = TRUE,
  legend.title = "H3 status × ecDNA",
  legend.labs = levels(df$strata_group),
  palette = c("#0072B2", "#0072B2", "#D55E00", "#D55E00"),
  linetype = c("solid", "dashed", "solid", "dashed")
)


ggsurvplot(
  fit,
  data = df,
  pval = TRUE,
  risk.table = TRUE,
  legend = "right",
  legend.title = "Groups"
) +
  ggplot2::annotate("text",
    x = 60, y = 0.85, label = "WT, no ecDNA",
    color = "#0072B2", hjust = 0
  )

ggsurvplot(
  fit,
  data = df,
  pval = TRUE,
  risk.table = TRUE,
  legend.title = "H3 status × ecDNA",
  legend = "right",
  risk.table.height = 0.25,
  censor = TRUE
)

ggforest(
  cox_interaction,
  data = df,
  main = "Cox model with ecDNA × H3K27 interaction",
  cpositions = c(0.02, 0.22, 0.4),
  fontsize = 1.0
)

cox_stratified <- coxph(
  Surv(os_months, os_event) ~ ecDNA_status + TP53 + H3G34,
  data = df,
  subset = H3K27 == "K27M"
)

summary(cox_stratified)

table(df$ecDNA_status, useNA = "ifany")
table(df$H3K27, useNA = "ifany")
table(df$ecDNA_H3K27, useNA = "ifany")



```
#Venn diagram
```{r}
library(ggvenn)

group1 <- df$TP53
group2 <- df$ecDNA_status

g1 <- as.logical(group1 == 1)
g2 <- as.logical(group2 == "ecDNA+")

keep <- !is.na(g1) & !is.na(g2)

g1 <- g1[keep]
g2 <- g2[keep]

set1 <- which(g1)
set2 <- which(g2)

venn_list <- list(
  TP53_positive = set1,
  ecDNA_positive  = set2
)

ggvenn(
  venn_list,
  fill_color = c("#0072B2", "#D55E00"),
  fill_alpha = 0.5,
  set_name_size = 4
)

data.frame(
  TP53_only = sum(g1 & !g2),
  ecDNA_only  = sum(!g1 & g2),
  Both        = sum(g1 & g2),
  Neither     = sum(!g1 & !g2)
)

tab <- table(
  TP53 = g1,
  ecDNA  = g2
)

tab

fisher_res <- fisher.test(tab)
fisher_res


```